% Nanda H Krishna's CV

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{
\item\small{
\textbf{#1}{ #2 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{{\Large Nanda H Krishna}} \\
Chennai, India
$\cdot$ +91 9841022137
$\cdot$ \href{mailto:nanda.harishankar@gmail.com}{nanda.harishankar@gmail.com}
$\cdot$ \href{mailto:nanda17093@cse.ssn.edu.in}{nanda17093@cse.ssn.edu.in} \\
\href{https://nandahkrishna.me}{nandahkrishna.me}
$\cdot$ \href{github.com/nandahkrishna}{github.com/nandahkrishna}
$\cdot$ \href{linkedin.com/in/nandahkrishna}{linkedin.com/in/nandahkrishna}
\end{tabular*}

\section{About}
I am an Undergraduate Student of Computer Science and Engineering interested in Machine Learning, Computer Vision, Applied CS, and research in these fields.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Sri Sivasubramaniya Nadar College of Engineering}{Chennai}
{B.E. Computer Science and Engineering; Affiliated to Anna University; GPA: 9.47 (3 semesters)}{2017 -- 2021}
\resumeItemListStart
\resumeItem{Activities \& Societies:}{Q! (Quiz Club), Lights Out Please (Theatre Club), English Literary Club, Competitive Programming Club, Google Developer Student Club}
\resumeItemListEnd
\resumeSubheading
{Vidya Mandir Senior Secondary School}{Chennai}
{High School: Computer Science; CBSE; Class X 10 CGPA; Class XII 96.6\% (483/500)}{2003 -- 2017}
\resumeItemListStart
\resumeItem{Activities \& Societies:}{Math Club, Chemistry Club, Darpan (Magazine) Editorial Team, Quiz, Sanskrit Drama}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Solarillion Foundation}{Chennai}
{Undergraduate Research Assistant}{Oct. 2018 - Present}
\resumeItemListStart
\resumeItem{Machine Learning Group:}
{Currently working on Movie Lifetime Prediction based on transactional data from a top multiplex in Chennai. Previously worked on Prediction of Flight Delay based on historical flight performance data and weather data.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\resumeSubHeadingListStart
\resumeItem{Machine Learning:}{scikit-learn, Keras, TensorFlow, PyTorch}
\resumeItem{Image Processing:}{OpenCV, scikit-image}
\resumeItem{Languages:}{Python, C, C++, Shell, Java, MATLAB, HTML, CSS, SQL}
\resumeItem{Frameworks:}{Numpy, Pandas, NetworkX, Matplotlib, Git (Version Control)}
\resumeItem{Hardware:}{Arduino, Raspberry Pi}
\resumeSubHeadingListEnd

\section{Publications}
\resumeSubHeadingListStart
\resumeItem{Species Recommendation using Machine Learning - GeoLifeCLEF 2019:}{Working Notes for GeoLifeCLEF 2019 to be published in CEUR-WS. 2019.}
\resumeSubHeadingListEnd

\section{Projects and Research}
\resumeSubHeadingListStart
\resumeItem{Movie Lifetime Prediction (Jan. 2019 - Present):}{Working on predicting the lifetime of a movie based on transaction data from a top multiplex in Chennai.}
\resumeItem{Measurement of Wheel Distances and Angles from Stereo Images (Aug. 2018 - Present):}{An industrial project to measure the distance and angles of tilt of a wheel using images captured by stereo cameras, using OpenCV and C++.}
\resumeItem{GeoLifeCLEF 2019 (Mar. 2019 - May. 2019):}{Worked on species recommendation using Machine Learning based on location and environmental variables.}
\resumeItem{Flight Delay Prediction using Machine Learning (Nov. 2018 - Jan. 2019):}{Worked on a machine learning based approach to predict arrival and departure delay of flights based on historical flight performance data and weather data.}
\resumeItem{WhacAR (Dec. 2018):}{Developed an AR game for Android using Sceneform and ARCore, written in Kotlin. Won the top team award at MLH Local Hack Day 2018.}
\resumeItem{Pokemon Go on Arduino (Jul. 2018):}{Developed a simple version of Pokemon Go using Arduino and IMU sensor.}
\resumeItem{brOS - Suite of Applications (Oct. 2016 - Dec. 2016):}{A suite of applications coded in C++, developed for the Class 12 Computer Science Project. Contains 4 applications (Clock, Calendar, Calculator, Notepad) and 4 games, and a customisable UI. Won the Best Project in Computer Science Award.}
\resumeSubHeadingListEnd

\section{Open Source Contributions}
\resumeSubHeadingListStart
\resumeItem{NetworkX:}{Created a module for group centrality measures in graphs, fixed documentation errors, helped in maintenance, reviewed pull requests.}
\resumeItem{Pandas:}{Helped in maintenance, removed specific handling for py.path.}
\resumeItem{DepHell:}{Modified command implementations, added tests.}
\resumeItem{Prefect:}{Standardised class repr for all classes, removed inconsistencies.}
\resumeItem{RxPY:}{Improved version maintenance and control using bumpversion.}
\resumeSubHeadingListEnd

\section{Courses and Certifications}
\resumeSubHeadingListStart
\resumeItem{Machine Learning:}{Stanford University, Coursera}
\resumeItem{Python for Data Science:}{UC San Diego, edX}
\resumeItem{Machine Learning Crash Course:}{Google AI}
\resumeItem{Linear Algebra:}{MIT 18.02 (OCW)}
\resumeItem{Embedded Software Development:}{Workshop at SSN College of Engineering}
\resumeItem{Blockchain and Hyperledger:}{Workshop at SSN College of Engineering}
\resumeItem{University Courses:}{Python Programming, C Programming, Mathematics - I and II, Discrete Mathematics, Probability and Queuing Theory, Data Structures, Object Oriented Programming, Design and Analysis of Algorithms, Digital Principles and System Design, Computer Architecture, Operating Systems, Database Management Systems}
\resumeSubHeadingListEnd

\section{Teaching, Talks and Workshops}
\resumeSubHeadingListStart
\resumeItem{Computational Thinking Workshop (2018):}{Organized a workshop introducing first year students to various aspects of Computer Science (at SSN).}
\resumeSubHeadingListEnd

\section{Achievements}
\resumeSubHeadingListStart
\resumeItem{}{Gold Medals and Merit Scholarship for securing Rank 1 in Semesters 1 \& 2}
\resumeItem{}{Winner, CodeStorm (Reverse Coding and Competitive Programming), CEG Abacus 2019}
\resumeItem{}{Top team at MLH Local Hack Day 2018, Chennai}
\resumeItem{}{ACM ICPC: 2017 Online Round Honorable Mention, 2018 KCG Chennai Provincial 5th Place}
\resumeItem{}{Award for Consistent Performance in Computer Science in Class 11 \& 12}
\resumeItem{}{Award for Best Project in Computer Science in Class 12}
\resumeSubHeadingListEnd

\section{Volunteering and Responsibilities}
\resumeSubHeadingListStart
\resumeItem{}{Organised Quiz Club events for SSN's Tech Fest and Cultural Fest}
\resumeSubHeadingListEnd

\section{Memberships}
ACM - Student Member $\cdot$ IEEE - Student Member

\section{Languages}
English $\cdot$ Tamil $\cdot$ Hindi $\cdot$ Sanskrit $\cdot$ Japanese $\cdot$ Korean $\cdot$ German

\section{Hobbies}
Languages $\cdot$ Poetry $\cdot$ Music $\cdot$ Anime $\cdot$ Manga $\cdot$ Asian TV Shows

\lfoot{\small Last Updated: 28 May 2019}

\end{document}